\documentclass{beamer}
\usetheme{Madrid}

\title{Failover Network Using Redundant Paths}
\subtitle{Using STP and HSRP}
\author{Your Name}
\date{\today}

\begin{document}

\begin{frame}
\titlepage
\end{frame}

\begin{frame}{Problem Statement}
\begin{itemize}
    \item In critical networks (hospitals, banks, universities), a single device or link failure can cause complete network outages.
    \item Downtime leads to service loss, data unavailability, and operational disruption.
    \item Redundant links without control protocols cause network loops and broadcast storms.
\end{itemize}
\end{frame}

\begin{frame}{Solution Path}
\begin{itemize}
    \item \textbf{Redundancy:} Create backup physical links between switches and routers.
    \item \textbf{Loop Prevention with STP:} 
    \begin{itemize}
        \item STP blocks redundant links during normal operation.
        \item STP unblocks backup links if primary fails, ensuring continuity.
    \end{itemize}
    \item \textbf{Gateway Redundancy with HSRP:}
    \begin{itemize}
        \item Configure two routers sharing a virtual IP.
        \item One router acts as Active, the other as Standby.
        \item Automatic gateway switch-over during failure.
    \end{itemize}
\end{itemize}
\end{frame}

\begin{frame}{Outcome}
\begin{itemize}
    \item \textbf{High Availability:} Continuous network operation even after device or link failure.
    \item \textbf{Automatic Recovery:} No manual intervention needed.
    \item \textbf{Network Resilience:} Reliable access to resources and services.
\end{itemize}
\end{frame}

\end{document}
