\documentclass{beamer}

% Theme and color
\usetheme{CambridgeUS}
\usecolortheme{dolphin}

% Packages
\usepackage{graphicx}
\usepackage{tikz}
\usepackage{lipsum}

% Background image on title page


\title{\textbf{Failover Network Using Redundant Paths}}
\subtitle{Implementing STP and HSRP}
\author{Your Name}
\institute{Computer Network Conference}
\date{\today}

\begin{document}

% Title slide
\begin{frame}[plain]
\titlepage
\end{frame}

% Clear background for other slides
\usebackgroundtemplate{}

\begin{frame}{Problem Statement}
\Large
\begin{itemize}
    \item In critical networks (hospitals, banks, universities), a single failure can shut down the entire system.
    \item Redundant links without control protocols cause loops and broadcast storms.
    \item Downtime results in service loss, financial cost, and reputation damage.
\end{itemize}
\end{frame}

\begin{frame}{Solution Path}
\Large
\textbf{Redundancy:} 
\begin{itemize}
    \item Create backup links between switches and routers.
\end{itemize}
\vspace{0.5cm}
\textbf{STP (Spanning Tree Protocol):}
\begin{itemize}
    \item Avoids loops by blocking redundant links.
    \item Automatically re-activates backup links if primary fails.
\end{itemize}
\vspace{0.5cm}
\textbf{HSRP (Hot Standby Router Protocol):}
\begin{itemize}
    \item Two routers share a virtual gateway IP.
    \item Active router forwards traffic; standby takes over if active fails.
\end{itemize}
\end{frame}

\begin{frame}{Expected Outcome}
\Large
\begin{itemize}
    \item \textbf{High Availability:} Continuous service even during failure.
    \item \textbf{Automatic Failover:} Fast and seamless recovery.
    \item \textbf{Enhanced Network Reliability:} Essential for mission-critical applications.
\end{itemize}
\end{frame}

\end{document}
